\documentclass{RecipePage}
\begin{document}
\recipeTitle{Pad See You with Chicken}
\recipeInfo{4 servings}{Unknown}{Unknown}
\hbox to 0.9\textwidth{
\vbox{
\hsize=0.4\textwidth
\begin{ingredients}
\item{3 tablespoons (45 milliliters) Chinese sweet soy sauce}
\item{1 tablespoon (15 milliliters) oyster sauce}
\item{2 tablespoons (30 milliliters) fish sauce}
\item{2 teaspoons (10 grams) sugar}
\item{1 1/2 cups (335 grams) broccoli florets}
\item{3 tablespoons (45 milliliters) vegetable oil}
\item{1 pound (450 grams) chicken breast, sliced thin}
\item{2 cloves garlic, minced}
\item{2 large eggs}
\item{4 cups (960 grams) fresh rice noodles, separated}
\item{1/2 teaspoon white pepper}
\end{ingredients}
}
\vbox{
\hsize=0.45\textwidth
\begin{instructions}
\item Combine the Chinese sweet soy sauce, oyster sauce, fish sauce and sugar in a small bowl and set it aside.
\item Place the broccoli florets in a bowl with about 1 tablespoon (15 milliliters) of water and cover with plastic wrap. Microwave for 1 1/2 minutes on high, then set aside until ready to use.
\item Heat the oil on high in a large skillet for about 1 minute. When you see the first wisps of white smoke, add the chicken and garlic to the pan and saute for about 1 minute or until the exterior of the chicken is mostly seared and opaque. Don't be scared to really scrape the bits off the pan before they burn.
\item Add in the eggs, then "cradle" the noodles in the eggs, tossing to coat the noodles with the egg.
\item Drain the broccoli and add, tossing it constantly until it starts to turn dark green, 1 to 2 minutes. Then add the sauce and stir constantly to combine for about 3 minutes until the noodles soak up the sauce and start to crisp slightly on the edges.
\item When the chicken is cooked through and the sauces are absorbed, sprinkle with white pepper and combine very well. 
\end{instructions}
}
}
\begin{tips}
\item Enjoy! :)
\end{tips}
\end{document}